---
title: "Mini Project 1 (Solutions)"
author: "Buddhika Jayawardana"
date: "2/1/2020"
output: html_document
---


### Section 1

1. In this problem we use the KNN classification method on the training data set and prodict the classes of the test data set. 
   a) knn() funtion was used for the K values = seq(1, 496, by = 1)
   b) Training and test error rates were calculated for defferent K values and they were ploted against K values as follows.
      
```{r pressure, echo=FALSE}


```
   c) Optimal value of K is found by finding the minimum value of test error rates and there were two K values that minimizes the test error rates, K = and K = . Associate training and test error rates were shown on the following table.
      optimal.point
      
   d) Since we had two K values that makes the test error rate minimize, corresponding decision boundaries were ploted seperatly as follows.



2. 1/5th of the data set e CIFAR-10 were used to classify using KNN method with K = 50, 100, 200, 300, 400. 
  a) Following table shows the error rates for defferent K values.
  
```{r pressure, echo=FALSE}
50     100    200    300    400 
0.7030 0.7210 0.7355 0.7505 0.7565 

```  
  
  b) Minimum error of test error rate was 0.7030 and the assosiate K value was 50. Bellow is the confusion metrix.
  
```{r pressure, echo=FALSE}
table(mod.test, y.test)
        y.test
mod.test   0   1   2   3   4   5   6   7   8   9
       0 112  16  34   9   6  12   6  12  18  11
       1   0   0   0   0   0   0   0   0   0   0
       2  12  11  45  32  17  33  22  33   5   6
       3   0   0   0   4   0   0   0   1   1   0
       4  37  64 108 109 121 105 109  97  28  71
       5   0   0   0   1   0  13   0   1   1   0
       6   5  35  14  29  12  19  38  14   7  12
       7   0   0   1   1   0   3   2  10   0   5
       8  49  65  13  17  12   9   9  32 130 101
       9   0   7   1   2   0   2   1   4   2  14

```  

  c) 
  
```{r pressure, echo=FALSE}
plot(ks, err.rate.test, xlab = "Number of nearest neighbors", ylab = "Test error rate", type = "b", ylim = range(c(err.rate.test)), col = "blue", pch = 20)

```    














